Demography and selection since maize domestication

### 2015-05-01 manuscript.tex
update

\section{Results}
\subsection{Patterns of variability differ between genic and
  nongenic regions of the genome}
Text goes here

@@

\begin{figure}[h]
%\vspace*{.05in}
\centering
\includegraphics[width=.5\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_unNeutralized}
\caption{Pairwise diversity surrounding synonymous and nonsynonymous
  substitutions in maize. Observe that the reduction of diversity
  surrounding nonsynonymous subsitutions is no more severe than the
  reduction of diversity surrounding synonymous substitutions. This
  equivalency suggests that hard sweeps are not a primary driver of
  maize diversity.}
\label{hardSweeps}
\end{figure}

>>>>

\section{Results}
\subsection{Patterns of variability differ between genic and
  nongenic regions of the genome}
Previous research of the maize domestication process has relied upon
observations drawn from genic DNA \textcolor{red}{(several references
  here)}. Our data were generated through whole genome sequencing,
which eliminated this constraint. Importantly, we observed substantial
differences in patterns of diversity between genic and non-genic regions
of the genome for both maize and teosinte. For maize, mean pairwise
diversity ($\pi$) within genes was significantly lower than at
positions at least 5kb away from genes (0.00668 within, 0.00691 away, p$<$2e-44). The same
pattern of significantly greater diversity outside of genes was observed in
teosinte, but to a larger extent. For teosinte we observed $\pi$
within genes to be 0.0088 and at least 5kb from genes it was 0.1153
(p$\approx$0). These obserrvations suggest that genes are not evolving
neutrally in maize or teosinte. Instead, some form of selection must
be reducing diversity within genes. Additionally, these observations
suggest that demographic inference, which relies on the assumption of
neutrally evolving DNA, will be more accurate if it is based on
observations from non-genic genetic material.

@@

\begin{figure}[b]
%\vspace*{.05in}
\centering
\includegraphics[width=.5\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_unNeutralized}
\caption{Pairwise diversity surrounding synonymous and nonsynonymous
  substitutions in maize. Observe that the reduction of diversity
  surrounding nonsynonymous subsitutions is no more severe than the
  reduction of diversity surrounding synonymous substitutions. This
  equivalency suggests that hard sweeps are not a primary driver of
  maize diversity.}
\label{hardSweeps}
\end{figure}
